Paper analysis

### 2025-03-26 Paper_analysis.Rmd
update site

```{r nexpmarg_int}
grid.arrange(
  int.nexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.nexpmarg.ntr_pland %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

@@

```{r sedmarg_int}
grid.arrange(
  int.sedexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.sedexpmarg.ann_agr_ed %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

@@

```{r qbmarg_int}
grid.arrange(
  int.qbmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.qbmarg.prn_agr_para_mn %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

>>>>

```{r nexpmarg_int}
grid.arrange(
  int.nexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.nexpmarg.ann_agr_pland %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

@@

```{r sedmarg_int}
grid.arrange(
  int.sedexpmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.sedexpmarg.lu_shdi %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```

@@

```{r qbmarg_int}
grid.arrange(
  int.qbmarg %>% plot() + ggtitle("Interaction strength") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  int.qbmarg.field_frac_cv %>% plot() + ggtitle("Pairwise interactions with strongest") + egg::theme_article() + theme(plot.title.position = "plot", axis.title.y = element_blank()),
  ncol = 2
)
```
